Optimal (Multiway) Spatial Joins

### 2024-05-27 msj.tex
yufei

In the {\em reporting version} of the problem, the goal is to output, for each point $p \in P$, all the rectangles $r \in R$ containing $p$, provided that at least one such $r$ exists. For example, in Figure~\ref{fig:guard}a, the output is $\set{(p_2: r_1, r_2), (p_3: r_2)}$. As shown in Appendix~\ref{app:bricks}, this can be achieved in $O(n \log n + \out)$ time, where $\out$ is the number of pairs $(p, r) \in P \times R$ such that $p \in r$.

\extraspacing {\bf Problem $\bm{\mathscr{B}}$.} The input involves a set $H$ of horizontal segments and a set $V$ of vertical segments. The goal is to report, for each segment $h \in H$, the leftmost point $p$ on $h$ such that $p$ is on some vertical segment in $V$. If $h$ does not intersect with any segment in $V$, report nothing for $h$. Figure~\ref{fig:probs}b gives an example where $H = \set{h_1, h_2, h_3}$ and $V = \set{v_1, v_2}$; the output is $\set{(h_1, p_1), (h_2, p_2)}$. This can be achieved in $O(n \log n)$ time where $n = |H| + |V|$, as shown in Appendix~\ref{app:bricks}.

\extraspacing {\bf Problem $\bm{\mathscr{C}}$.} The input involves a set $H$ of horizontal segments and a set $R$ of rectangles. The goal is to report, for each segment $h \in H$, the rightmost point $p$ on $h$ such that $p$ is covered by at least one left-end covering rectangle of $h$ in $R$ --- formally, for $h = [x_1, x_2] \times y$, we aim to find the maximum $x \in [x_1, x_2]$ such that at least one rectangle $r \in R$ covers both the point $(x_1, y)$ and the point $(x, y)$. If the point $p$ exists (i.e., $h$ has at least one left-end covering rectangle in $R$), we should output a tuple $(h, p)$; otherwise, output nothing for $h$. Figure~\ref{fig:probs}c gives an example where $H = \set{h_1, h_2}$ and $R$ includes the three rectangles shown; the output is $\set{(h_1, p_1), (h_2, p_2)}$. In Appendix~\ref{app:bricks}, we explain how to solve the problem in $O(n \log n)$ time where $n = |H| + |R|$.

\extraspacing {\bf Problem $\bm{\mathscr{D}}$.} The input involves a set $H$ of horizontal segments and a set $R$ of rectangles. In the {\em find-lowest} version of the problem, the goal is to report, for each rectangle $r \in R$, the lowest segment in $\cross_H(r)$ (see \eqref{eqn:cross}). If no segment in $H$ crosses $r$, output nothing for $r$.  Figure~\ref{fig:probs}d gives an example where $H = \set{h_1, h_2, h_3}$ and $R = \set{r_1, r_2}$; the output is $\set{(r_1, h_3), (r_2, h_2)}$. This can be achieved in $O(n \log n)$ time where $n = |H| + |R|$ as shown
In Appendix~\ref{app:bricks}.

@@

In the {\em find-all-sorted} version of the problem, the goal is to report, for each rectangle $r \in R$, the entire $\cross_H(r)$ sorted by y-coordinate. Formally, if $\cross_H(r) = \set{h_1, h_2, ..., h_z}$ (for some $z \ge 1$), we output $(r: h_1, h_2, ..., h_z)$, provided that $y_i \ge y_{i-1}$ for each $i \in [2, z]$ where $y_i$ (resp., $y_{i-1}$) is the y-projection of $h_i$ (resp., $h_{i-1}$). In the example of Figure~\ref{fig:probs}d, the output is $\set{(r_1: h_3, h_2), (r_2: h_2, h_1)}$. In Appendix~\ref{app:bricks}, we explain how to solve the problem in $O(n \log n + \out)$ time where $\out$ is the number of pairs $(h, r) \in H \times R$ such that $h$ crosses $r$.

>>>>

In the {\em reporting version} of Problem $\mathscr{A}$, the goal is to output, for each point $p \in P$, all the rectangles $r \in R$ containing $p$. In Figure~\ref{fig:guard}a, for instance, the output is $\set{(p_1, \emptyset), (p_2: r_1, r_2), (p_3: r_2)}$. As shown in Appendix~\ref{app:bricks}, this can be achieved in $O(n \log n + \out)$ time, where $\out$ is the number of pairs $(p, r) \in P \times R$ such that $p \in r$.

\extraspacing {\bf Problem $\bm{\mathscr{B}}$.} The input involves a set $H$ of horizontal segments and a set $V$ of vertical segments. The goal is to report, for each segment $h \in H$, the leftmost point $p$ on $h$ such that $p$ is on some vertical segment in $V$. If $h$ does not intersect with any segment in $V$, report nothing for $h$. Figure~\ref{fig:probs}b gives an example where $H = \set{h_1, h_2, h_3}$ and $V = \set{v_1, v_2}$; the output is $\set{(h_1, p_1), (h_2, p_2)}$. This problem can be solved in $O(n \log n)$ time where $n = |H| + |V|$, as shown in Appendix~\ref{app:bricks}.

\extraspacing {\bf Problem $\bm{\mathscr{C}}$.} The input involves a set $H$ of horizontal segments and a set $R$ of rectangles. The goal is to report, for each segment $h \in H$, the rightmost point $p$ on $h$ such that $p$ is covered by at least one left-end covering rectangle of $h$ in $R$ --- formally, for $h = [x_1, x_2] \times y$, we aim to find the maximum $x \in [x_1, x_2]$ such that at least one rectangle $r \in R$ covers both the point $(x_1, y)$ and the point $(x, y)$. If the point $p$ exists (i.e., $h$ has at least one left-end covering rectangle in $R$), we should output a tuple $(h, p)$; otherwise, output nothing for $h$. Figure~\ref{fig:probs}c gives an example where $H = \set{h_1, h_2}$ and $R$ includes the three rectangles shown; the output is $\set{(h_1, p_1), (h_2, p_2)}$. This problem can be solved in in $O(n \log n)$ time where $n = |H| + |R|$, as shown in Appendix~\ref{app:bricks}.

\extraspacing {\bf Problem $\bm{\mathscr{D}}$.} The input involves a set $H$ of horizontal segments and a set $R$ of rectangles. In the {\em find-lowest} version of the problem, the goal is to report, for each rectangle $r \in R$, the lowest segment in $\cross_H(r)$ (see its definition in \eqref{eqn:cross}). If no segment in $H$ crosses $r$, output nothing for $r$.  Figure~\ref{fig:probs}d gives an example where $H = \set{h_1, h_2, h_3}$ and $R = \set{r_1, r_2}$; the output is $\set{(r_1, h_3), (r_2, h_2)}$. This can be achieved in $O(n \log n)$ time where $n = |H| + |R|$, as shown in Appendix~\ref{app:bricks}.

@@

In the {\em find-all-sorted} version of the problem, the goal is to report, for each rectangle $r \in R$, the entire $\cross_H(r)$ sorted by y-coordinate. Formally, if $\cross_H(r) = \set{h_1, h_2, ..., h_z}$ for some $z \ge 1$, we output $(r: h_1, h_2, ..., h_z)$, provided that $y_i \ge y_{i-1}$ for each $i \in [2, z]$ where $y_i$ (resp., $y_{i-1}$) is the y-coordinate of $h_i$ (resp., $h_{i-1}$). In the example of Figure~\ref{fig:probs}d, the output is $\set{(r_1: h_3, h_2), (r_2: h_2, h_1)}$. In Appendix~\ref{app:bricks}, we explain how to solve the problem in $O(n \log n + \out)$ time where $\out$ is the number of pairs $(h, r) \in H \times R$ such that $h$ crosses $r$.
